A thesis draft

### 2018-11-14 res/sections/25-Tests.tex
Add subfigures

It is worth saying that Docker metrics are generally more precise than the 
Virtual Box one: Docker allows to inspect the container and to gain startup and 
shutdown times with a precision of millseconds, while to gather this 
information for VirtualBox instances we had to use the command line utility 
\verb!time!, that registered timing with a precision of hundredths of a 
second. Nonetheless, this didn't influence the test too much. To avoid possible 
outliers we perfomed the test $100$ times. With this $N$, the total time spent 
by the Virtual Machines to boot up was of $2000$\todo{Update with the real 
value} seconds, while with containers the same number of start ups resulted in a 
total of $1.xx$\todo{Update with the real value}. % Insert graphs, explain the 
%problems of virtual machines
\begin{figure}[t] % TODO set subfigure and put the pie plot on the right!
 \centering
 \includegraphics[scale=0.5]{docker_vs_vmBarplotGraph}
 \caption[Docker vs Virtual Box barplot results]{Docker vs Virtual Box barplot 
results. It is possible to see how the total time to start up a virtual machine 
through Virtual Box is very high compared to the time required to the overall 
Docker containers to boot. A single VirtualBox instance requires on average 20 
seconds to boot up, while a container requires, on average, only 0.02 seconds. 
The main reason behind this difference, as already explained in other parts of 
this thesis, it is caused by the guest's kernel that has to initialized itself, 
before starting any program. On Docker, instead, the kernel is the same of the 
host, so the only operations needed are to isolate the program from the rest of 
the OS and add it to the process list.}
 \label{chap:tests:sec:dockervsvb:img:barplot}
\end{figure}

>>>>

It is worth saying that Docker metrics are generally more precise than the 
Virtual Box one: Docker allows to inspect the container and to gain startup and 
shutdown times with a precision of millseconds, while to gather this 
information for VirtualBox instances we had to use the command line utility 
\verb!time!, that registered timing with a precision of hundredths of a 
second. Nonetheless, this didn't influence the test too much. To avoid possible 
outliers we perfomed the test $100$ times. With this $N$, the total time spent 
by the Virtual Machines to boot up was of $2000$\todo{Update with the real 
value} seconds, while with containers the same number of start ups resulted in a 
total of $1.xx$\todo{Update with the real value}. % Insert graphs, explain the 
%problems of virtual machines

\begin{figure}[t] % TODO fix image dimensions!
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{docker_vs_vmBarplotGraph}
        \caption{Barplot between Virtual Box and Docker startup times.}
        \label{chap:tests:sec:dockervsvb:img:barplot}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{docker_vs_vmBoxplotGraph}
        \caption{Boxplot between Virtual Box and Docker with values normalized 
in $0-1$ range.}
        \label{chap:tests:sec:dockervsvb:img:boxplot}
    \end{subfigure}
    \caption[Virtual Box vs Docker start up comparison]{In these graphs it is 
possible to see how the total time to start up a virtual machine through Virtual 
Box is very high compared to the time required to the overall Docker containers 
to boot. A single VirtualBox instance requires on average 20 seconds to boot up, 
while a container requires, on average, only 0.02 seconds. The main reason 
behind this difference, as already explained in other parts of this thesis, it 
is caused by the guest's kernel that has to initialized itself, before starting 
any program. On Docker, instead, the kernel is the same of the host, so the only 
operations needed are to isolate the program from the rest of the OS and add it 
to the process list.}
    \label{chap:tests:sec:dockervsvb:subimg:plots}
\end{figure}
